### 2024-01-19 tesis_Ashish/Chapter5/chapter5.tex
update

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%)}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.2 \\
        Ghosts \& satellites & 0.15 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.33 \\
        Beam-beam effects & 0.37 \\
        Length scale & 0.12 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.2 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.7 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.5 \\
        Cross-detector linearity & 0.54 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.5 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%)}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.5 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.4 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

### 2024-01-19 tesis_Ashish/Chapter8/chapter8.tex
update

In Chapter 5, significant results from the PCC luminosity measurement during Run 3 (2022) are outlined. %The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented. These uncertainties encompass a range of factors including calibration (1.3\%), integration (0.8\%), and other specific sources such as beam current (0.2\%), orbit drift (0.3\%), and cross-detector linearity (0.54\%), culminating in a total uncertainty of \(1.5\%\).

>>>>

In Chapter 5, significant results from the PCC luminosity measurement during Run 3 (2022) are outlined. %The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented. These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%), culminating in a total uncertainty of \(1.4\%\).
